Incentivizing Exploration with Unbiased History

### 2018-11-02 3level.tex
About the notation for number of groups
C_0,N_0 => \estC, \estN
define macro \NG for number of groups

The middle level consists of $N_2$ disjoint subsets of $T_2$ agents each, called \emph{second-level groups}. Each second-level group $S$ has the following property:
\begin{align}\label{eq:group-defn}
\text{all nodes in $S$ are connected to the same nodes outside of $S$, but not to one another.}
\end{align}

The full-disclosure paths in the first level are also split into $N_2$ disjoint subsets, called \emph{first-level groups}. Each first-level group consists of $T_1$ full-disclosure paths, for the total of $T_1\cdot N_2\cdot \fdpL$ rounds in the first layer. There is a 1-1 correspondence between first-level groups $S_1$ and second-level groups $S_2$, whereby each agent $t\in S_2$ observes the full history from the corresponding group $S_1$. More formally, agent $t$ is connected to the last node of each full-disclosure path in $S_1$. In other words, this agent receives message
    $m_t = \SubH{V(S_1)}$,
where $V(S_1)$ is the set of all rounds in $S_1$.
\end{construction}

@@

  \draw [decorate,decoration={brace,amplitude=10pt,aspect=0.33},xshift=0pt,yshift=0pt] (10,1.8) -- (0,1.8) node [black,pos=0.33,xshift = 0cm,yshift=-0.6cm] {$N_2$ groups};

@@

\begin{theorem}
\label{thm:3level}
For two arms, the three-level policy
achieves regret
\[ \reg(T) \leq O\left( T^{4/7}\, \log T \right).\]
This is achieved with parameters
    $T_1 = T^{4/7}\log^{-1/7}(T)$,
    $N_2 = 2^{10}\log(T)$, and
    $T_2 = T^{6/7}\log^{-5/7}(T)$.
\end{theorem}

@@

\begin{lemma}[Medium gap]\label{3levelmedium}
  All agents pull arm 1 in the third level, when $\Delta$ satisfies
%  \[
%  \Delta\in \left[
%   2\left(\sqrt{\frac{4\log(T)}{S\fdpN[1]T_1}} +
%    \sqrt{\frac{4\log(T)}{S\fdpN[2]T_1}}\right),
% 2\left(\sqrt{\frac{4\log(T)}{\fdpN[1]T_1}} +
%        \sqrt{\frac{4\log(T)}{\fdpN[2]T_1}}\right),
%    \right)
%  \]
\[ \textstyle \Delta\in \left[
    4\,\sum_{a\in\A}\; \conf{N_2\cdot \fdpN[a]\cdot T_1},\quad
    4\,\sum_{a\in\A}\; \conf{\fdpN[a]\cdot T_1}
 \right] \]
\end{lemma}

Finally, the \emph{small gap} case, when  $\Delta$ is between
$\tilde\Omega(\sqrt{1/T_2})$ and $\tilde O(\sqrt{1/(N_2\, T_1)})$ 
is more challenging since even aggregating the data from all $N_2$
first-level groups is not sufficient for identify the best arm. 
We need to ensure that both arms continue to be explored in the second level. 
To achieve this, we leverage \event[4], which implies 
that each arm $a$ has a first-level group $s_a$ where it gets ``lucky", in the sense that its empirical mean reward is slightly higher than $\mu_a$, while the empirical mean reward of the other arm is slightly lower than its true mean. Since the
deviations are in the order of $\Omega(\sqrt{1/T_1})$, and Assumption~\ref{ass:embehave} guarantees the agents' reward estimates are also within $\Omega(\sqrt{1/T_1})$ of the empirical means, the sub-history
from this group $s_a$ ensures that all agents in the respective second-level group prefer arm $a$. Therefore, both arms are pulled at least $T_2$ times in the second level, which in turn gives the following guarantee:

\begin{lemma}[Small gap]\label{3levelsmallcase}
  All agents pull arm 1 in the third level, when $\Delta$ satisfies
%  \[
%    \Delta\in \left( 3\sqrt{\frac{2\log(T)}{T_2}},
%      2\left(\sqrt{\frac{4\log(T)}{S \fdpN[1]T_1}} +
%        \sqrt{\frac{4\log(T)}{S \fdpN[2]T_1}}\right) \right)
%  \]
\[ \textstyle 
    \Delta\in \left( 3\sqrt{2}\cdot\conf{T_2},\quad
      4\,\sum_{a\in\A}\; \conf{N_2\cdot \fdpN[a]\cdot T_1}
\right)
\]
\end{lemma}

\paragraph{Wrapping up: proof of \Cref{thm:3level}. } In negligible
gap case, the stated regret bound holds regardless of what the algorithm does. In the large gap case, the regret only comes from the
first level, so it is upper-bounded by the total number of agents in this level, which is 
    $N_2\cdot \GdT \cdot T_1 = O(T^{4/7} \log T)$. 
In both intermediate cases, it suffices to bound the regret from the
first and second levels, so
\[ \textstyle 
\reg(T) \leq (N_2\,T_1\cdot \GdT + N_2\, T_2) 
\cdot 4\,\sum_{a\in\A}\; \conf{\fdpN[a]\cdot T_1}
= O(T^{4/7} \log^{6/7}(T)).
\]
Therefore, we obtain the stated regret bound in all cases.

>>>>

The middle level consists of $\NG$ disjoint subsets of $T_2$ agents each, called \emph{second-level groups}. Each second-level group $S$ has the following property:
\begin{align}\label{eq:group-defn}
\text{all nodes in $S$ are connected to the same nodes outside of $S$, but not to one another.}
\end{align}

\jmcomment{$\NG$ is also used in Lemma 3.6. We need to find another notation. And I think it should be something without subscript 2. It's generally a property of the whole construction. How about $\NG$.}

The full-disclosure paths in the first level are also split into $\NG$ disjoint subsets, called \emph{first-level groups}. Each first-level group consists of $T_1$ full-disclosure paths, for the total of $T_1\cdot \NG\cdot \fdpL$ rounds in the first layer. There is a 1-1 correspondence between first-level groups $S_1$ and second-level groups $S_2$, whereby each agent $t\in S_2$ observes the full history from the corresponding group $S_1$. More formally, agent $t$ is connected to the last node of each full-disclosure path in $S_1$. In other words, this agent receives message
    $m_t = \SubH{V(S_1)}$,
where $V(S_1)$ is the set of all rounds in $S_1$.
\end{construction}

@@

  \draw [decorate,decoration={brace,amplitude=10pt,aspect=0.33},xshift=0pt,yshift=0pt] (10,1.8) -- (0,1.8) node [black,pos=0.33,xshift = 0cm,yshift=-0.6cm] {$\NG$ groups};

@@

\begin{theorem}
\label{thm:3level}
For two arms, the three-level policy
achieves regret
\[ \reg(T) \leq O\left( T^{4/7}\, \log T \right).\]
This is achieved with parameters
    $T_1 = T^{4/7}\log^{-1/7}(T)$,
    $\NG = 2^{10}\log(T)$, and
    $T_2 = T^{6/7}\log^{-5/7}(T)$.
\end{theorem}

@@

\begin{lemma}[Medium gap]\label{3levelmedium}
  All agents pull arm 1 in the third level, when $\Delta$ satisfies
%  \[
%  \Delta\in \left[
%   2\left(\sqrt{\frac{4\log(T)}{S\fdpN[1]T_1}} +
%    \sqrt{\frac{4\log(T)}{S\fdpN[2]T_1}}\right),
% 2\left(\sqrt{\frac{4\log(T)}{\fdpN[1]T_1}} +
%        \sqrt{\frac{4\log(T)}{\fdpN[2]T_1}}\right),
%    \right)
%  \]
\[ \textstyle \Delta\in \left[
    4\,\sum_{a\in\A}\; \conf{\NG\cdot \fdpN[a]\cdot T_1},\quad
    4\,\sum_{a\in\A}\; \conf{\fdpN[a]\cdot T_1}
 \right] \]
\end{lemma}

Finally, the \emph{small gap} case, when  $\Delta$ is between
$\tilde\Omega(\sqrt{1/T_2})$ and $\tilde O(\sqrt{1/(\NG\, T_1)})$ 
is more challenging since even aggregating the data from all $\NG$
first-level groups is not sufficient for identify the best arm. 
We need to ensure that both arms continue to be explored in the second level. 
To achieve this, we leverage \event[4], which implies 
that each arm $a$ has a first-level group $s_a$ where it gets ``lucky", in the sense that its empirical mean reward is slightly higher than $\mu_a$, while the empirical mean reward of the other arm is slightly lower than its true mean. Since the
deviations are in the order of $\Omega(\sqrt{1/T_1})$, and Assumption~\ref{ass:embehave} guarantees the agents' reward estimates are also within $\Omega(\sqrt{1/T_1})$ of the empirical means, the sub-history
from this group $s_a$ ensures that all agents in the respective second-level group prefer arm $a$. Therefore, both arms are pulled at least $T_2$ times in the second level, which in turn gives the following guarantee:

\begin{lemma}[Small gap]\label{3levelsmallcase}
  All agents pull arm 1 in the third level, when $\Delta$ satisfies
%  \[
%    \Delta\in \left( 3\sqrt{\frac{2\log(T)}{T_2}},
%      2\left(\sqrt{\frac{4\log(T)}{S \fdpN[1]T_1}} +
%        \sqrt{\frac{4\log(T)}{S \fdpN[2]T_1}}\right) \right)
%  \]
\[ \textstyle 
    \Delta\in \left( 3\sqrt{2}\cdot\conf{T_2},\quad
      4\,\sum_{a\in\A}\; \conf{\NG\cdot \fdpN[a]\cdot T_1}
\right)
\]
\end{lemma}

\paragraph{Wrapping up: proof of \Cref{thm:3level}. } In negligible
gap case, the stated regret bound holds regardless of what the algorithm does. In the large gap case, the regret only comes from the
first level, so it is upper-bounded by the total number of agents in this level, which is 
    $\NG\cdot \GdT \cdot T_1 = O(T^{4/7} \log T)$. 
In both intermediate cases, it suffices to bound the regret from the
first and second levels, so
\[ \textstyle 
\reg(T) \leq (\NG\,T_1\cdot \GdT + \NG\, T_2) 
\cdot 4\,\sum_{a\in\A}\; \conf{\fdpN[a]\cdot T_1}
= O(T^{4/7} \log^{6/7}(T)).
\]
Therefore, we obtain the stated regret bound in all cases.

### 2018-11-02 llevel-overview.tex
.
define macro \NG for number of groups

\xhdr{Connecting structures between levels with $S=2$.} In our 3-level
policy, the second level has $S = \Theta(\log(T))$ groups. We do so to
ensure that in the small gap case (Lemma \ref{3levelsmallcase}), with
high probability, both arms are pulled enough times in the second
level. The argument relies on the fact that agents in different
second-level groups observe disjoint histories of the first level and
the independent randomness in first level groups guarantees each arm
$a$ to have a ``lucky'' second-level group such that agents in that
group all pull arm $a$ with high probability.

Simply generalizing this idea to an $L$-level policy would give us a $S$-ary tree like structure and the first level will have $S^{L-1}$ groups. It incurs an extra $S^{\Omega(L)}$ factor in the regret. If we use $\log\log(T)$ levels as in Theorem \ref{thm:llevel-1}, this factor super poly-logarithmic. If we use $\log(T)/\log\log(T)$ levels as in Theorem \ref{thm:llevel-2}, this factor goes up to polynomial in $T$.

@@

For each level, our $L$-level policy has $S^2$ groups for some $S = \Theta(\log(T))$. The groups in the $l$-th level are labeled as $G_{l,u,v}$ for $u,v\in[S]$. For any $l \in \{2,...,L\}$ and $u,v,w\in [S]$, agents in group $G_{l,u,v}$ see the history of agents in group $G_{l-1,v,w}$ (and by transitivity all agents in levels below $l-1$). See Figure \ref{fig:llevel-connecting} for a graphical view (as space limit, we only show 3 levels and 4 groups in each level). This connecting structure has three nice properties: \\
(i) The number of groups does not grow with $L$ and stays as $S^2 = \Theta(\log^2(T))$ in each level. Having these groups only incurs a $\Theta(\log^2(T))$ multiplicative factor to the regret.\\
(ii) Consider groups $G_{l-1,1,v},G_{l-1,2,v},...,G_{l-1,S,v}$ (e.g. $G_{l-1,1,1}$ and $G_{l-1,2,1}$ with red circles in the figure ) as a set of groups indexed by $l-1$ and $v$. The agents in a set of groups see the same history. They get ``lucky'' for some arm at the same time.\\
(iii) For each set of groups in level $l-1$, agents in level $l$ see the history of agents in one of these groups. Therefore, for each arm $a$, we just need one set of groups in level $l-1$ to get ``lucky'' and then all agents in level $l$ will see enough pulls of arm $a$.

@@

When we extend the 3-level policy to an $L$-level policy, we have such boundary case for each intermediate level. Moreover, the worry mentioned above does not get naturally resolved as in some of these boundary cases, the ratios between the upper and lower bounds of the gap rise from $\Theta(\sqrt{\log(T)})$ to $\Theta(\log(T))$. The reason for such rise is that, except the first level, we don't have good enough guarantee of the number of pulls of each arm. For example, in Figure \ref{fig:llevel-connecting}, when we talk about having enough arm $a$ pulls in the history observed by agents in $G_{l,1,1}$, it could be that  only agents in group $G_{l-1,1,1}$ are pulling arm $a$ and it also could be that most agents in groups $G_{l-1,1,1},G_{l-1,1,2},...,G_{l-1,1,S}$ are pulling arm $a$. Therefore our estimate of the number of arm $a$ pulls can be off by an $S=\Theta(\log(T))$ multiplicative factor. This finally makes the boundary cases harder to deal with.

In our $L$-level policy, after understanding the boundary cases well, we resolve this problem by introducing an additional type of groups: $\Gamma$-groups. For each $l \in [L], u,v \in [S]$, we create a $\Gamma$-group $\Gamma_{l,u,v}$. Agents in $\Gamma_{l,u,v}$ observe the same history as the one observed by agents in $G_{l,u,v}$ and the number of agents in $\Gamma_{l,u,v}$ is $\Theta(\log(T)$ times the number of agents in $G_{l,u,v}$. The main difference between the $G$-groups and $\Gamma$-groups is that the history of $\Gamma$ groups in level $l$ is not sent to agents in level $l+1$ but agents in higher levels. When we are in the boundary case in which we don't have good guarantees about the $l+1$ level agents' pulls, the new construction makes sure that agents in levels higher than $l+1$ get enough pulls of each arm and all pull the best arm. 
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:

>>>>

\xhdr{Connecting structures between levels} In our 3-level
policy, the second level has $\NG = \Theta(\log(T))$ groups. We do so to
ensure that in the small gap case (Lemma \ref{3levelsmallcase}), with
high probability, both arms are pulled enough times in the second
level. The argument relies on the fact that agents in different
second-level groups observe disjoint histories of the first level and
the independent randomness in first level groups guarantees each arm
$a$ to have a ``lucky'' second-level group such that agents in that
group all pull arm $a$ with high probability.

Simply generalizing this idea to an $L$-level policy would give us a $\NG$-ary tree like structure and the first level will have $\NG^{L-1}$ groups. It incurs an extra $\NG^{\Omega(L)}$ factor in the regret. If we use $\log\log(T)$ levels as in Theorem \ref{thm:llevel-1}, this factor super poly-logarithmic. If we use $\log(T)/\log\log(T)$ levels as in Theorem \ref{thm:llevel-2}, this factor goes up to polynomial in $T$.

@@

For each level, our $L$-level policy has $\NG^2$ groups for some $\NG = \Theta(\log(T))$. The groups in the $l$-th level are labeled as $G_{l,u,v}$ for $u,v\in[\NG]$. For any $l \in \{2,...,L\}$ and $u,v,w\in [\NG]$, agents in group $G_{l,u,v}$ see the history of agents in group $G_{l-1,v,w}$ (and by transitivity all agents in levels below $l-1$). See Figure \ref{fig:llevel-connecting} for a graphical view (as space limit, we only show 3 levels and 4 groups in each level). This connecting structure has three nice properties: \\
(i) The number of groups does not grow with $L$ and stays as $\NG^2 = \Theta(\log^2(T))$ in each level. Having these groups only incurs a $\Theta(\log^2(T))$ multiplicative factor to the regret.\\
(ii) Consider groups $G_{l-1,1,v},G_{l-1,2,v},...,G_{l-1,\NG,v}$ (e.g. $G_{l-1,1,1}$ and $G_{l-1,2,1}$ with red circles in the figure ) as a set of groups indexed by $l-1$ and $v$. The agents in a set of groups see the same history. They get ``lucky'' for some arm at the same time.\\
(iii) For each set of groups in level $l-1$, agents in level $l$ see the history of agents in one of these groups. Therefore, for each arm $a$, we just need one set of groups in level $l-1$ to get ``lucky'' and then all agents in level $l$ will see enough pulls of arm $a$.

@@

When we extend the 3-level policy to an $L$-level policy, we have such boundary case for each intermediate level. Moreover, the worry mentioned above does not get naturally resolved as in some of these boundary cases, the ratios between the upper and lower bounds of the gap rise from $\Theta(\sqrt{\log(T)})$ to $\Theta(\log(T))$. The reason for such rise is that, except the first level, we don't have good enough guarantee of the number of pulls of each arm. For example, in Figure \ref{fig:llevel-connecting}, when we talk about having enough arm $a$ pulls in the history observed by agents in $G_{l,1,1}$, it could be that  only agents in group $G_{l-1,1,1}$ are pulling arm $a$ and it also could be that most agents in groups $G_{l-1,1,1},G_{l-1,1,2},...,G_{l-1,1,\NG}$ are pulling arm $a$. Therefore our estimate of the number of arm $a$ pulls can be off by an $\NG=\Theta(\log(T))$ multiplicative factor. This finally makes the boundary cases harder to deal with.

In our $L$-level policy, after understanding the boundary cases well, we resolve this problem by introducing an additional type of groups: $\Gamma$-groups. For each $l \in [L], u,v \in [\NG]$, we create a $\Gamma$-group $\Gamma_{l,u,v}$. Agents in $\Gamma_{l,u,v}$ observe the same history as the one observed by agents in $G_{l,u,v}$ and the number of agents in $\Gamma_{l,u,v}$ is $\Theta(\log(T)$ times the number of agents in $G_{l,u,v}$. The main difference between the $G$-groups and $\Gamma$-groups is that the history of $\Gamma$ groups in level $l$ is not sent to agents in level $l+1$ but agents in higher levels. When we are in the boundary case in which we don't have good guarantees about the $l+1$ level agents' pulls, the new construction makes sure that agents in levels higher than $l+1$ get enough pulls of each arm and all pull the best arm. 
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:
